---
title: "R Notebook"
output: html_notebook
---

Michael Hornsby Exercise Set 7

# Number 1
This code chunk below creates my funtion

I spent about 5 hours trying to figure out why my one fuction would not return the 
data set 'my_data' to the global environment.  Seeing as how I couldn't figure that out, 
I just combined everything into one function to give the closest possible answer.

*I've copied your code below to try to create a pure function.*

```{r}
#Load the car package
library(car)

my.function <- function(xvar, yvar, p) {
  
# Create the model and residuals
  
model <- lm(yvar ~ xvar)

residuals <- residuals(model)

my_data <- as.data.frame(cbind(xvar, yvar, residuals))

# Create an order vector and order the residuals from largest to smallest
order_vector <- order(abs(my_data$residuals), decreasing = TRUE)

my_data <- my_data[order_vector,]

# Create the logical vector, add it to my data set, and return the data set

logical_vector <- (c(rep(TRUE, p), rep(FALSE,length(my_data$xvar) - p)))

my_data$outcome <- logical_vector

my_data <- data.frame(my_data)

return(my_data)

}

# Now the call

data("iris")
the_data <- my.function(iris$Sepal.Length, iris$Petal.Length, 15)

# It worked for me! Look at the_data and you have everything you need.

```




*You should not put your scatterplot in your function. This should be drawn*
*outside your function. Notice, for example, how you had to put labels in your*
*function. These will be invalid if you change the data set. (-2)*

```{r}
#Load the car package
library(car)

my.function <- function(xvar, yvar, p) {
  
# Create the model and residuals
  
model <- lm(yvar ~ xvar)

residuals <- residuals(model)

my_data <- as.data.frame(cbind(xvar, yvar, residuals))

# Create an order vector and order the residuals from largest to smallest
order_vector <- order(abs(my_data$residuals), decreasing = TRUE)

my_data <- my_data[order_vector,]

# Create the logical vector, add it to my data set, and return the data set

logical_vector <- (c(rep(TRUE, p), rep(FALSE,length(my_data$xvar) - p)))

my_data$outcome <- logical_vector

my_data <- data.frame(my_data)

# This creates the scatterplot with the regline.

scatterplot(x = my_data$xvar,
            y = my_data$residuals,
            regLine = TRUE,
            groups = my_data$outcome,
            legend = FALSE,
            smooth = FALSE,
            xlab = "Sepal Length",
            ylab = "Residual",
            main = "Highlighted Largest Residuals")

print(my_data)
}

# load the iris data and run the function.  The iris data has 150 observations, 
# so I used p to be 15, or 10% of those  I used Sepal Length as x and 
# Petal Length as y.
data("iris")

my.function(iris$Sepal.Length, iris$Petal.Length, 15)
```

I couldn't figure out how to have the one regline with 2 highlighted colors.
The by.groups arguement for the scatterplot function didn't really work how the 
help page suggested in that regard.
ALso, I only added the print within the function at the end specifically 
because I couldn't get it to return to the environment properly and I wanted to 
demonstrade it provide the appropriate logical outcome.
I'm not really happy with how this script turned out, but I'll use a stressbuster for 
a regrade if necessary.